---
output: github_document
---

# mlr3featsel

_mlr3featsel_ adds filters, feature selection methods and embedded feature selection methods of algorithms to _mlr3_.

[![Travis build status](https://travis-ci.org/mlr-org/mlr3featsel.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3featsel)
[![CRAN status](https://www.r-pkg.org/badges/version/mlr3featsel)](https://cran.r-project.org/package=mlr3featsel)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3featsel/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3featsel?branch=master)

## Installation

```{r eval = FALSE}
remotes::install_github("mlr-org/mlr3featsel")
```

## Filters

* `stats::cor(method = "spearman")`
* `stats::cor(method = "pearson")`
* `stats::kruskal.test()`
* `stats::var()`
* `AUC` -> `Metrics::auc`
* `FSelectorRcpp::information.gain(type = "gainratio")`
* `FSelectorRcpp::information.gain(type = "infogain")`
* `FSelectorRcpp::information.gain(type = "symuncert")`
* `praznik::CMIM()`
* `praznik::DISR()`
* `praznik::JMI()`
* `praznik::JMIM()`
* `praznik::MIM()`
* `praznik::NJMIM()`

```{r}
library(mlr3featsel)
as.data.table(mlr_filters)
```


#### Public Methods

* `.$calculate()`: Calculates Filter values
* `.$filter()`: filters the task by a given criterion

* `.$scores`: Filter score values
* `.$filtered_task`: Filtered task

## Implemented "wrapper methods"

## Algorithm-embedded methods

All learners that support the property "importance" can be used to create a filter based on their respective implemented variable importance measure.

```{r}
library(mlr3)
library(mlr3learners)
mlr_learners$get("classif.ranger")$properties
```

Some learner need to have their variable importance measure activated during learner creation.
For example, to use the "impurity" measure of Random Forest via the _ranger_ package:

```{r error=TRUE}
task = mlr_tasks$get("iris")
lrn = mlr_learners$get("classif.ranger", 
  param_vals = list(importance = "impurity"))

filter = FilterVariableImportance$new(learner = lrn)
filter$calculate(task)
head(as.data.table(filter), 3)
```
